---
title: "The `sl3` R Package"
subtitle: "Modern Super Learning with Pipelines"
author: "[Jeremy Coyle](https://github.com/jeremyrcoyle), [Nima
  Hejazi](https://nimahejazi.org), [Ivana
  Malenica](https://github.com/podTockom), [Oleg
  Sofrygin](https://github.com/osofr)"
date: "`r lubridate::now()`"
output:
  xaringan::moon_reader:
    lib_dir: libs
    chakra: libs/remark-latest.min.js
    css: ["default", "custom.css"]
    nature:
      highlightStyle: zenburn
      highlightLines: true
      navigation: {
        scroll: false
      }
---

```{r knitr_setup, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 4.5, dpi = 300,
                      fig.cap = "", fig.align = "center")
showtext::showtext.opts(dpi = 300)
```

# Accessing these slides

--

### View them online:

* [https://jeremyrcoyle.github.io/sl3/slides/sl3-slides.html](https://jeremyrcoyle.github.io/sl3/slides/sl3-slides.html)

* here's a shortened URL: [https://goo.gl/fAEhqJ](https://goo.gl/fAEhqJ)

???

- This talk will focus on introducing the new `sl3` R package, which provides a
modern implementation of the Super Learner algorithm [@vdl2007super], a method
for performing stacked regressions [@breiman1996stacked], combined with
covariate screening and cross-validation.

---
class: inverse, center, middle

# Core `sl3` Design Principles

---

# `sl3` Architecture

All of the classes defined in `sl3` are based on the R6 framework, which brings
a newer object-oriented paradigm to the R language.

## Core classes

- `sl3_Task`, for defining a machine learning problem. These objects keep track
  of the task data, as well as what variables play what roles in the machine
  learning problem. These are easily created by `make_sl3_Task`.

--

- `Lrnr_base`, a base class for defining machine learning algorithms, as well as
  _fits_ for those algorithms to particular `sl3_Task`s. Different learning
  algorithms are defined in classes that inherit from this base class.

--

- `Pipeline`, a set of learners to be fit _sequentially_, where the fit from one
  learner is used to define the task for the next learner. These are a special
  kind of learner derived from `Lrnr_base`.

--

- `Stack`, like `Pipelines`, except in that learners are trained
  _simultaneously_, so that their predictions can be either combined or
  compared. These are a special kind of learner derived from `Lrnr_base`.

???

- Probably good to point out that cross-validating a `Stack` allows for an
  included `Pipeline` to be subjected to CV in the same way as other learners
  (seriously awesome feature).
- Might be worth mentioning the basic differences between core OOP concepts, for
  example classes, objects, methods, fields, inheritance, etc.
- Because all learners inherit from `Lrnr_base`, they have many features in
  common, and can be used interchangeably.
- All learners define three main methods: `train`, `predict`, and `chain`.
- `Pipeline` allows for covariate screening and model fitting to be subjected to
  the same cross-validation process, necessary for Super Learning.

---

# Object Oriented Programming (OOP)

- The key concept of OOP is that of an object, a collection of data and
  functions that corresponds to some conceptual unit. Objects have two main
  types of elements: _fields_ and _methods_.
  
--

- _fields_ are information about an object.

--

- _methods_ are actions an object can perform.

--

- Objects are members of _classes_, which define what those specific fields and
  methods are. Classes can inherit elements from other classes.
  
--

- `sl3` is designed using basic OOP principles and the R6 OOP framework, in
  which methods and fields of a class object are accessed using the `$`
  operator.

---
class: inverse, center, middle

# The Anatomy of `sl3`

---

# Get the package

- Currently, installation from the `master` branch is the only option:

```{r install_pkg, message=FALSE, eval=FALSE}
devtools::install_github("jeremyrcoyle/sl3")
```

```{r prelims-pkgs, message=FALSE, echo=FALSE}
set.seed(49753)
library(data.table)
library(dplyr)
library(origami)
library(SuperLearner)
```

--

- Of course, the package will be available on CRAN. An initial release is
  forthcoming.

--

To start using `sl3`, let's load the package:

```{r prelims-pkg, message=FALSE}
library(sl3)
```

---

# A "toy" data set

We can't do any model fitting without data. We use data from the Collaborative
Perinatal Project (CPP) to illustrate the features of `sl3` as well as its
proper usage. For convenience, the data is included with the `sl3` R package.

```{r prelims-data, message=FALSE}
# load example data set
data(cpp_imputed)

# here are the covariates we are interested in and, of course, the outcome
covars <- c("apgar1", "apgar5", "parity", "gagebrth", "mage", "meducyrs",
            "sexn")
outcome <- "haz"
```

???

- Next, we'll walk through analyzing some data.

---

# Setting up `sl3_Task`s I

Recall that a `sl3_Task` is the core structure that holds the data set and
specifications to be respected in the estimation/modeling procedure.

```{r sl3-task-setup, message=FALSE}
task <- make_sl3_Task(data = cpp_imputed, covariates = covars,
                      outcome = outcome, outcome_type="continuous")
```

--

- We use the `make_sl3_Task` method to create a new `sl3_Task`, called `task`.

- Here, we specified the underlying data, `cpp_imputed`, and vectors indicating
  which varaibles to use as covariates and outcomes.

- We also specified an `outcome_type`, here "continuous", indicating if the outcome corresponds to continuous or categorical (or another type of) data.
--

## `sl3_Task` Options

- `make_sl3_Task` supports a range of options in order to facilitate the
  articulation of more advanced specifics informative of the machine learning
  problem.
  
- For example, we can specify the id, weights, and offset nodes.

---

# Setting up `sl3_Task`s II

Let's take a look at the `task` that we set up:

```{r sl3-task-nodes, message=FALSE}
task
```

---

# Learners I: Introduction

- `Lrnr_base` is the base class for defining machine learning algorithms, as
  well as fits for those algorithms to particular `sl3_Task`s.

--

- Different machine learning algorithms are defined in classes that inherit from
  `Lrnr_base`.
  
--
  
- For instance, the `Lrnr_glm` class inherits from `Lrnr_base`, and defines a
  learner that fits generalized linear models.
  
--

- Learner objects can be constructed from their class definitions using the
  `make_learner` function:

```{r}
# make learner object
lrnr_glm <- make_learner(Lrnr_glm)
```

---

# Learners II: Core Methods

- All learners inherit from `Lrnr_base`, so they have many features in common,
  and can be used interchangeably.

--

- All learners define three main methods: `train`, `predict`, and `chain`.

--

- The first, `train`, takes a `sl3_task` object, and returns a `learner_fit`,
  which has the same class as the learner that was trained:

```{r, message=FALSE}
# fit learner to task data
lrnr_glm_fit <- lrnr_glm$train(task)

# verify that the learner is fit
lrnr_glm_fit$is_trained
```

--

- Here, we fit the learner to the CPP task we defined above. Both `lrnr_glm` and
  `lrnr_glm_fit` are objects of class `Lrnr_glm`, although the former defines a
  learner and the latter defines a fit of that learner.

--

- We can distiguish between the learners and learner fits using the `is_trained`
  field, which is true for fits but not for learners.

---

# Learners III: Prediction

- Now that we've fit a learner, we can generate predictions using the `predict`
  method:

```{r}
# get learner predictions
preds <- lrnr_glm_fit$predict(task)
head(preds)
```

--

- Here, we specified `task` as the task for which we wanted to generate
  predictions. If we had omitted this, we would have gotten the same predictions
  because `predict` defaults to using the task provided to `train` (called the
  training task). Alternatively, we could have provided a different task for
  which we want to generate predictions.

--

- The final important learner method, `chain`, will be discussed later, when we
  discuss __learner composition__. As with `sl3_Task`, learners have a variety
  of fields and methods we haven't discussed here.

---

# Learners IV: Properties

- Learners have _properties_ that indicate what features they support. You can
  use `sl3_list_properties` to get a list of all properties supported by at
  least one learner.

--

You can then use `sl3_list_learners` to find learners supporting any
set of properties:

```{r sl3-list-learner}
sl3_list_properties()

sl3_list_learners(c("binomial", "offset"))
```

--

Defining a `sl3` learner that uses the `SL.glmnet` wrapper from `SuperLearner`:

```{r SuperLearner Wrapper}
lrnr_sl_glmnet <- make_learner(Lrnr_pkg_SuperLearner, "SL.glmnet")
```

???

- In most cases, using wrappers from `SuperLearner` will not be as efficient as
  their native `sl3` counterparts. If your favorite learner is missing from
  `sl3`, please consider adding it by following the "Defining New Learners"
  vignette.

---

# Learners V: Parameters

- In general, learners can be instantiated without providing any additional
  parameters.

--

- We've tried to provide sensible defaults for each learner; however, if you
  would like to modify the learners' behavior, you may do so by instantiating
  learners with different parameters.

--

`sl3` Learners support some common parameters that work with all learners for
which they are applicable:

* `covariates`: subsets covariates before fitting. This allows different
  learners to be fit to the same task with different covariate subsets.

* `outcome_type`: overrides the `task$outcome_type`. This allows different
  learners to be fit to the same task with different outcome_types.

* `...`: abitrary parameters typically passed directly to the internal learner
  method. The documentation for each learner will direct to the appropriate
  function documentation for the learner method.

---
class: inverse, center, middle

# Composing Learners in `sl3`

---

# Pipelines I

- **A pipeline is a set of learners to be fit _sequentially_, where the fit from
  one learner is used to define the task for the next learner.**

--

- There are many ways in which a learner can define the task for the downstream
  learner. The `chain` method defined by learners defines how this will work.
  Let's look at the example of pre-screening variables.

--

- Below, we generate a screener object based on the `SuperLearner` function
  `screen.corP` and fit it to our task. Inspecting the fit, we see that it
  selected a subset of covariates:

```{r sl3-fit-screener, message=FALSE}
screen_cor <- Lrnr_pkg_SuperLearner_screener$new("screen.corP")
screen_fit <- screen_cor$train(task)
print(screen_fit)
```

---

# Pipelines II

- Now, `chain` may be called on this learner fit to define a downstream task:

```{r sl3-chain-screener}
screened_task <- screen_fit$chain()
print(screened_task)
```

---

# Pipelines III

- As with `predict`, we can omit a task from the call to `chain`, in which case
  the call defaults to using the same task that was used for training.

--

- We can see that the chained task reduces the covariates to the subset selected
  by the screener. We can fit this new task using the `lrnr_glm` we defined
  above:

```{r sl3-glm-on-screened}
screened_glm_fit <- lrnr_glm$train(screened_task)
screened_preds <- screened_glm_fit$predict()
head(screened_preds)
```

--

- The `Pipeline` class automates this process. It takes an arbitrary number of
  learners and fits them sequentially, training and chaining each one in turn.
  Since `Pipeline` is a learner like any other, it shares the same interface.

---

# Pipelines IV

- We can define a pipeline using `make_learner`, and use `train` and `predict`
  just as we did before:

```{r sl3-define-pipeline}
sg_pipeline <- make_learner(Pipeline, screen_cor, lrnr_glm)
sg_pipeline_fit <- sg_pipeline$train(task)
sg_pipeline_preds <- sg_pipeline_fit$predict()
head(sg_pipeline_preds)
```

--

- We see that the pipeline returns the same predictions as manually training
  `glm` on the chained task from the screening learner.

---

# Pipelines V

```{r sl3-viz-pipeline, echo=FALSE}
dt <- delayed_learner_train(sg_pipeline, task)
plot(dt, color=FALSE, height="500px")
```


---

# Stacks I

- **Like `Pipeline`s, `Stack`s combine multiple learners. `Stack`s train
  learners _simultaneously_, so that their predictions can be either combined or
  compared.**

--

- Again, `Stack` is just a special learner and so has the same interface as all
  other learners:

```{r sl3-stack}
stack <- make_learner(Stack, lrnr_glm, sg_pipeline)
stack_fit <- stack$train(task)
stack_preds <- stack_fit$predict()
head(stack_preds)
```

--

- Above, we've defined and fit a `stack` comprised of a simple `glm` learner as
  well as a pipeline that combines a screening algorithm with that same learner.

???

- We could have included any abitrary set of learners and pipelines, the latter
  of which are themselves just learners.

- We can see that the `predict` method now returns a matrix, with a column for
  each learner included in the stack.

--- 

---
# Stacks II

```{r sl3-viz-stack, echo=FALSE}
dt <- delayed_learner_train(stack, task)
plot(dt, color=FALSE, height="500px")
```

---

# But What About Cross-validation?

_Almost forgot! CV is necessary in order to honestly evaluate our models and
avoid overfitting. We provide facilities for easily doing this, based on the
[`origami` package](https://github.com/jeremyrcoyle/origami)._

--

- The `Lrnr_cv` learner wraps another learner and performs training and
  prediction in a cross-validated fashion, using separate training and
  validation splits as defined by `task$folds`.

--

- Below, we define a new `Lrnr_cv` object based on the previously defined
  `stack` and train it and generate predictions on the validation set:

```{r sl3-cv-stack}
cv_stack <- Lrnr_cv$new(stack)
cv_fit <- cv_stack$train(task)
cv_preds <- cv_fit$predict()
```

---

# Cross-validation (continued...)

- We can also use the special `Lrnr_cv` function `cv_risk` to estimate
  cross-validated risk values:

```{r sl3-cv-risk}
risks <- cv_fit$cv_risk(loss_squared_error)
print(risks)
```

--

- In this example, we don't see much difference between the two learners,
  suggesting the addition of the screening step in the pipeline learner didn't
  improve performance much.

---

# Cross-validation (continued...)

```{r sl3-viz-cv-stack, echo=FALSE}
dt <- delayed_learner_train(cv_stack, task)
plot(dt, color=FALSE, height="500px")
```
---
class: inverse, center, middle

# Putting it all together: Super Learning

---

# Super Learner I: Meta-Learners

- _We can combine `Pipeline`s, `Stack`s, and `Lrnr_cv` to easily define a Super
  Learner_.

--

- Using some of the objects we defined in the above examples, this becomes a
  nearly trivial operation:

```{r sl3-metalearner-glm}
metalearner <- make_learner(Lrnr_nnls)
cv_task <- cv_fit$chain()
ml_fit <- metalearner$train(cv_task)
```

--

- Here, we used a special learner, `Lrnr_nnls`, for the meta-learning step. This
  fits a non-negative least squares meta-learner. **Note that any learner can be
  used as a meta-learner.**

---

# Super Learner II: Pipelines

- The Super Learner finally produced is defined as a pipeline with the learner
  stack trained on the full data and the meta-learner trained on the
  validation-set predictions.

--

- Below, we use a special behavior of pipelines: if all objects passed to a
  pipeline are learner fits (i.e., `learner$is_trained` is `TRUE`), the result
  will also be a fit:

```{r sl3-define-SuperLearner}
sl_pipeline <- make_learner(Pipeline, stack_fit, ml_fit)
sl_preds <- sl_pipeline$predict()
head(sl_preds)
```

---

# Super Learner III: `Lrnr_sl`

- **A Super Learner may be fit in a more streamlined manner using the `Lrnr_sl`
  learner.**

--

- For simplicity, we will use the same set of learners and meta-learning
  algorithm as we did before:

```{r sl3-Lrnr_sl}
sl <- Lrnr_sl$new(learners = stack,
                  metalearner = metalearner)
sl_fit <- sl$train(task)
lrnr_sl_preds <- sl_fit$predict()
head(lrnr_sl_preds)
```

--

- We can see that this generates the same predictions as the more hands-on
  definition we encountered previously.

???

- Worth mentioning that the flexibility offered by our design allows us to
  invoke the Super Learner algorithm, but we can also do a lot more...

---
class: inverse, center, middle

# Computing with `delayed`

---

# Delayed I

- For large datasets, fitting a Super Learner can be extremely time-consuming.

--

- To alleviate this complication, we've developed a specialized parallelization
  framework `delayed` that parallelizes across these tasks in a way that takes
  into account their inter-dependent nature.

--

- Consider a Super Learner with three learners:

```{r sl3-delayed-sl}
lrnr_rf <- make_learner(Lrnr_randomForest)
lrnr_glmnet <- make_learner(Lrnr_glmnet)
sl <- Lrnr_sl$new(learners = list(lrnr_glm, lrnr_rf, lrnr_glmnet),
                  metalearner = metalearner)
```

--

- We can plot the network of tasks required to train this Super Learner:

```{r sl3-delayed-plot, eval=FALSE}
delayed_sl_fit <- delayed_learner_train(sl, task)
plot(delayed_sl_fit)
```

---

# Delayed II

```{r sl3-delayed-plot-actual, echo=FALSE}
delayed_sl_fit <- delayed_learner_train(sl, task)
plot(delayed_sl_fit, color = TRUE, height="500px")
```


---

# Delayed III

- **shiny demo**
- `delayed` then allows us to parallelize the procedure across these tasks using
  the [`future`](https://github.com/HenrikBengtsson/future) package.

- *n.b.*, This feature is currently experimental and hasn't yet been throughly
  tested on a range of parallel backends.

--

- Performance comparisons can be found in the "SuperLearner Benchmarks" vignette
  that accompanies this package.

???

- Fitting a Super Learner is composed of many different training and prediction
  steps, as the procedure requires that the learners in the stack and the
  meta-learner be fit on cross-validation folds and on the full data.

- For more information on specifying `future` `plan`s for parallelization, see
  the documentation of the [`future`](https://github.com/HenrikBengtsson/future)
  package.

---
class: center, middle

# Thanks!

We have a great team: Jeremy Coyle, Nima Hejazi, Ivana Malenica, Oleg Sofrygin.

Slides created via the R package
[**xaringan**](https://github.com/yihui/xaringan).

Powered by [remark.js](https://remarkjs.com),
[**knitr**](http://yihui.name/knitr), and
[R Markdown](https://rmarkdown.rstudio.com).
