---
always_allow_html: true
output:
  rmarkdown::github_document
bibliography: "inst/REFERENCES.bib"
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# R/`sl3`: modern Super Learning with pipelines

[![Travis-CI Build Status](https://travis-ci.com/tlverse/sl3.svg?branch=master)](https://travis-ci.com/tlverse/sl3)
[![Appveyor Build Status](https://ci.appveyor.com/api/projects/status/hagh8vidrdeacr7f?svg=true)](https://ci.appveyor.com/project/tlverse/sl3)
[![Coverage Status](https://img.shields.io/codecov/c/github/tlverse/sl3/master.svg)](https://codecov.io/github/tlverse/sl3?branch=master)
[![CRAN](http://www.r-pkg.org/badges/version/sl3)](http://www.r-pkg.org/pkg/sl3)
[![CRAN downloads](https://cranlogs.r-pkg.org/badges/sl3)](https://CRAN.R-project.org/package=sl3)
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![License: GPL v3](https://img.shields.io/badge/License-GPL%20v3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0)
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.3558317.svg)](https://doi.org/10.5281/zenodo.3558317)

> A modern implementation of the Super Learner algorithm for ensemble learning
> and model stacking

__Authors:__ [Jeremy Coyle](https://github.com/jeremyrcoyle), [Nima
Hejazi](https://nimahejazi.org), [Ivana
Malenica](https://github.com/podTockom), [Oleg
Sofrygin](https://github.com/osofr)

---

## What's `sl3`?

`sl3` is a modern implementation of the Super Learner algorithm of
@vdl2007super. The Super Learner algorithm performs ensemble learning in one of
two fashions:

1. The _discrete_ Super Learner can be used to select the best prediction
   algorithm from among a supplied library of machine learning algorithms
   ("learners" in the `sl3` nomenclature) -- that is, the discrete Super Learner
   is the single learning algorithm that minimizes the cross-validated risk with
   respect to an appropriate loss function.
2. The _ensemble_ Super Learner can be used to assign weights to a set of
   specified learning algorithms (from a user-supplied library of such
   algorithms) so as to create a combination of these learners that minimizes
   the cross-validated risk with respect to an appropriate loss function. This
   notion of weighted combinations has also been referred to as _stacked
   regression_ [@breiman1996stacked] and _stacked generalization_
   [@wolpert1992stacked].

---

## Installation

<!--
For standard use, we recommend installing the package from
[CRAN](https://cran.r-project.org/) via

```{r cran-installation, eval = FALSE}
install.packages("sl3")
```
-->

Install the _most recent version_ from the `master` branch on GitHub via
[`remotes`](https://CRAN.R-project.org/package=remotes):

```{r gh-master-installation, eval = FALSE}
remotes::install_github("tlverse/sl3")
```

Past stable releases may be located via the
[releases](https://github.com/tlverse/sl3/releases) page on GitHub and may be
installed by including the appropriate major version tag. For example,

```{r gh-version-installation, eval = FALSE}
remotes::install_github("tlverse/sl3@v1.3.5")
```

To contribute, check out the `devel` branch and consider submitting a pull
request.

---

## Issues

If you encounter any bugs or have any specific feature requests, please [file an
issue](https://github.com/tlverse/sl3/issues).

---

## Examples

`sl3` makes the process of applying screening algorithms, learning algorithms,
combining both types of algorithms into a stacked regression model, and
cross-validating this whole process essentially trivial. The best way to
understand this is to see the `sl3` package in action:

```{r sl3-simple-example, message=FALSE, warning=FALSE}
set.seed(49753)
library(tidyverse)
library(data.table)
library(SuperLearner)
library(origami)
library(sl3)

# load example data set
data(cpp)
cpp <- cpp %>%
  dplyr::filter(!is.na(haz)) %>%
  mutate_all(~ replace(., is.na(.), 0))

# use covariates of intest and the outcome to build a task object
covars <- c("apgar1", "apgar5", "parity", "gagebrth", "mage", "meducyrs",
            "sexn")
task <- sl3_Task$new(cpp, covariates = covars, outcome = "haz")

# set up screeners and learners via built-in functions and pipelines
slscreener <- Lrnr_pkg_SuperLearner_screener$new("screen.glmnet")
glm_learner <- Lrnr_glm$new()
screen_and_glm <- Pipeline$new(slscreener, glm_learner)
SL.glmnet_learner <- Lrnr_pkg_SuperLearner$new(SL_wrapper = "SL.glmnet")

# stack learners into a model (including screeners and pipelines)
learner_stack <- Stack$new(SL.glmnet_learner, glm_learner, screen_and_glm)
stack_fit <- learner_stack$train(task)
preds <- stack_fit$predict()
head(preds)
```

---

## Learner Properties

You can find the properties that sl3 learners support in the table below:

```{r warning=FALSE, echo = FALSE, message = FALSE}
library(sl3)
library(kableExtra)

all_properties <- sl3_list_properties()

get_all_learners <- function() {
  # search for objects named like sl3 learners
  learner_names <- apropos("^Lrnr_")
  learners <- mget(learner_names, inherits = TRUE)

  # verify that learner inherits from Lrnr_base (and is therefore an actual
  # sl3 Learner)
  is_learner_real <- sapply(learners, `[[`, "inherit") == "Lrnr_base"
  return(learners[which(is_learner_real)])
}
all_learners <- get_all_learners()

# get a list where each element is a list of properties of a particular learner
get_learner_class_properties <- function(learner_class) {
  return(learner_class$private_fields$.properties)
}
learner_property_lst <- lapply(all_learners, get_learner_class_properties)

# get a list where each element is a list of True/False's indicating whether a learner has a property or not
get_learner_class_properties_ownership <- function(properties) {
  return(sl3_list_properties() %in% unlist(properties))
}
learner_property_ownership_mat <- lapply(learner_property_lst, get_learner_class_properties_ownership)

get_learner_name <- function(learner_class) {
  return(learner_class$classname)
}
learner_names <- lapply(all_learners, get_learner_name)

# generate the data matrix, whose columns are properties and rows are learner names
final_mat <- matrix(unlist(learner_property_ownership_mat), nrow = length(learner_property_ownership_mat), ncol = length(sl3_list_properties()), byrow = TRUE)
dimnames(final_mat) <- list(unlist(learner_names), sl3_list_properties())
final_mat.df <- as.data.frame(final_mat)

char_final_mat.df <- ifelse(final_mat.df == TRUE, "√", "x")
kable(char_final_mat.df) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  scroll_box(width = "100%", height = "200px", fixed_thead = T)
```

---

## Contributions

Contributions are very welcome. Interested contributors should consult our
[contribution
guidelines](https://github.com/tlverse/sl3/blob/master/CONTRIBUTING.md) prior to
submitting a pull request.

---

## Citation

After using the `sl3` R package, please cite the following:

        @manual{coyle2019sl3,
          author = {Coyle, Jeremy R and Hejazi, Nima S and Malenica, Ivana and
            Sofrygin, Oleg},
          title = {{sl3}: Modern Pipelines for Machine Learning and {Super
            Learning}},
          year = {2019},
          howpublished = {\url{https://github.com/tlverse/sl3}},
          note = {{R} package version 1.3.5},
          url = {https://doi.org/10.5281/zenodo.3558317},
          doi = {10.5281/zenodo.3558317}
        }

---

## License

&copy; 2017-2019 [Jeremy R. Coyle](https://github.com/jeremyrcoyle), [Nima S.
Hejazi](https://nimahejazi.org), [Ivana
Malenica](https://github.com/podTockom), [Oleg
Sofrygin](https://github.com/osofr)

The contents of this repository are distributed under the GPL-3 license. See
file `LICENSE` for details.

---

## References

