---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# R/`sl3`: new and improved Super Learning

[![Travis-CI Build Status](https://travis-ci.org/jeremyrcoyle/sl3.svg?branch=master)](https://travis-ci.org/jeremyrcoyle/sl3) 
[![Build status](https://ci.appveyor.com/api/projects/status/25reu5wdhrwj9qgy?svg=true)](https://ci.appveyor.com/project/jeremyrcoyle/sl3)
[![Coverage Status](https://img.shields.io/codecov/c/github/jeremyrcoyle/sl3/master.svg)](https://codecov.io/github/jeremyrcoyle/sl3?branch=master) 
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/latest/wip.svg)](http://www.repostatus.org/#wip)
[![License: GPL v3](https://img.shields.io/badge/License-GPL%20v3-blue.svg)](http://www.gnu.org/licenses/gpl-3.0)

> A modern implementation of the Super Learner ensemble learning / stacking
> algorithm

__Authors:__ Jeremy Coyle, Nima Hejazi, Oleg Sofrygin, Ivana Malenica

---

## Description

...

---

## Installation

<!--
For standard use, we recommend installing the package from
[CRAN](https://cran.r-project.org/) via

```{r cran-installation, eval = FALSE}
install.packages("sl3")
```
-->

Install the most recent _stable release_ from GitHub via
[`devtools`](https://www.rstudio.com/products/rpackages/devtools/):

```{r gh-master-installation, eval = FALSE}
devtools::install_github("jeremyrcoyle/sl3")
```

<!--
To contribute, install the _development version_ from GitHub via
[`devtools`](https://www.rstudio.com/products/rpackages/devtools/):

```{r gh-develop-installation, eval = FALSE}
devtools::install_github("jeremyrcoyle/sl3", ref = "develop")
```
-->

---

## Issues

If you encounter any bugs or have any specific feature requests, please [file an
issue](https://github.com/jeremyrcoyle/sl3/issues).

---

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
#library(sl3)
```

---

## Contributions

It is our hope that `sl3` will grow to be widely used for... To that end,
contributions are very welcome, though we ask that
interested contributors consult our [`contribution
guidelines`](https://github.com/jeremyrcoyle/sl3/blob/master/CONTRIBUTING.md)
prior to submitting a pull request.

---

&copy; 2017 [Jeremy R. Coyle](https://github.com/jeremyrcoyle), [Nima S.
Hejazi](https://github.com/nhejazi), [Oleg Sofrygin](https://github.com/osofr),
[Ivana Malenica](https://github.com/podTockom)

The contents of this repository are distributed under the GPL-3 license. See
file `LICENSE` for details.
