---
title: "Modern Machine Learning in R"
author: "Jeremy Coyle, [Nima Hejazi](https://nimahejazi.org), Ivana Malenica,
  Oleg Sofrygin"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
bibliography: intro_sl3_refs.bib
vignette: >
  %\VignetteIndexEntry{Modern Machine Learning in R}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, echo=FALSE, results='hide'}
library(sl3)
```

## Introduction

The `sl3` package provides a modern framework for machine learning. This
includes the Super Learner algorithm [@vdl2007super], a method for performing
stacked regressions [@breiman1996stacked], combined with covariate screening and
cross-validation. `sl3` uses an Object Oriented Programming (OOP) approach and
leverages
[`R6`](https://cran.r-project.org/web/packages/R6/vignettes/Introduction.html)
classes to define both _Tasks_ (machine learning problems) and _Learners_
(machine learning algorithms that attempt to solve those problems) in a way that
is both flexible and extensible. The design of `sl3` owes a lot to the
`SuperLearner` and `mlr` packages, which also provide unified frameworks for
Super Learning and machine learning, respectively.

### Example Data

Throughout this vignette, we use data from the Collaborative Perinatal Project
(CPP) to illustrate the features of `sl3` as well as its proper usage. For
convenience, we've included an imputed version of this dataset in the `sl3`
package. Below, we load some useful packages, load the `cpp_imputed` dataset,
and define the variables (columns) from the data set we're interested in:

```{r prelims, message = FALSE}
set.seed(49753)

# packages we'll be using
library(data.table)
library(SuperLearner)
library(origami)
library(sl3)

# load example data set
data(cpp_imputed)

# here are the covariates we are interested in and, of course, the outcome
covars <- c("apgar1", "apgar5", "parity", "gagebrth", "mage", "meducyrs",
            "sexn")
outcome <- "haz"
```


### Basics of Object Oriented Programming

As mentioned above, `sl3` is designed using basic OOP principles and the
[`R6`](https://cran.r-project.org/web/packages/R6/vignettes/Introduction.html)
OOP framework. While we've tried to make it easy to use `sl3` without worrying
much about OOP, it is helpful to have some intuition about how `sl3` is
structured. In this section, we briefly outline some key concepts from OOP.
Readers familiar with OOP basics are invited to skip this section. The key
concept of OOP is that of an _object_, a collection of data and functions that
corresponds to some conceptual unit. Objects have two main types of elements,
_fields_, which can be thought of as nouns, are information about an object, and
_methods_, which can be thought of as verbs, are actions an object can perform.
Objects are members of _classes_, which define what those specific fields and
methods are. Classes can _inherit_ elements from other classes (sometimes called
_base classes_) -- accordingly, classes that are similar, but not exactly the
same, can share some parts of their definitions.

Many different implementations of OOP exist, with variations in how these
concepts are implemented and used. R has several different implementations,
including S3, S4, reference classes, and R6. `sl3` uses the
[`R6`](https://cran.r-project.org/web/packages/R6/vignettes/Introduction.html)
implementation. In R6, methods and fields of a class object are accessed using
the `$` operator. The next section explains how these concepts are used in `sl3`
to model machine learning problems and algorithms.

## `sl3` objects

### Tasks

The `sl3_Task` class defines machine learning problems. An `sl3_Task` object
keeps track of the task data, as well as what variables play what roles in the
machine learning problem. We can see an example of that here, using the `cpp`
dataset described above:

```{r sl3-task-create}
task <- make_sl3_Task(data = cpp_imputed, covariates = covars,
                      outcome = outcome)
```

We use the `make_sl3_Task` method to create a new `sl3_Task`, called `task`.
Here, we specified the underlying data, `cpp_imputed`, and vectors indicating
which varaibles to use as covariates and outcomes.

Let's take a look at this object:

```{r sl3-task-examine}
task
```

In addition to the simple usage demonstrated above, `make_sl3_Task` supports a
range of options in order to facilitate the proper articulation of more advanced
specifics potentially informative of the machine learning problem of interest.
For example, we can specify the `id`, `weights`, and `offset` nodes listed
above. These additional features are documented in the help for
[`sl3_Task`](../help/sl3_Task).

## Learners

`Lrnr_base` is the base class for defining machine learning algorithms, as well
as _fits_ for those algorithms to particular `sl3_Task`s. Different machine
learning algorithms are defined in classes that inherit from `Lrnr_base`. For
instance, the `Lrnr_glm` class inherits from `Lrnr_base`, and defines a learner
that fits generalized linear models. We will use the term _learners_ to refer to
the family of classes that inherit from `Lrnr_base`. Learner objects can be
constructed from their class definitions using the `make_learner` function:

```{r sl3-make_learner}
# make learner object
lrnr_glm <- make_learner(Lrnr_glm)
```

Because all learners inherit from `Lrnr_base`, they have many features in
common, and can be used interchangeably. All learners define three main methods:
`train`, `predict`, and `chain`. The first, `train`, takes a `sl3_task` object,
and returns a learner_fit, which has the same class as the learner that was
trained:

```{r sl3-learner-train}
# fit learner to task data
lrnr_glm_fit <- lrnr_glm$train(task)

# verify that the learner is fit
lrnr_glm_fit$is_trained
```

Here, we fit the learner to the CPP task we defined above. Both `lrnr_glm` and
`lrnr_glm_fit` are objects of class `Lrnr_glm`, although the former defines a
learner and the latter defines a fit of that learner. We can distiguish between
the learners and learner fits using the `is_trained` field, which is true for
fits but not for learners.

Now that we've fit a learner, we can generate predictions using the `predict`
method:

```{r sl3-learner-predict}
# get learner predictions
preds <- lrnr_glm_fit$predict(task)
head(preds)
```

Here, we specified `task` as the task for which we wanted to generate
predictions. If we had omitted this, we would have gotten the same predictions
because `predict` defaults to using the task provided to `train` (called the
training task). Alternatively, we could have provided a different task for which
we want to generate predictions.

The final important learner method, `chain`, will be discussed below, in the
section on __learner composition__. As with `sl3_Task`, learners have a variety
of fields and methods we haven't discussed here. More information on these is
available in the help for [`Lrnr_base`](../help/Lrnr_base).

### Finding Learners

Learners have _properties_ that indicate what features they support. You can use
`sl3_list_properties` to get a list of all properties supported by at least one
learner. You can then use `sl3_list_learners` to find learners supporting any
set of properties. For example:

```{r sl3-list-learner}
sl3_list_properties()

sl3_list_learners(c("binomial", "offset"))
```

The list of supported learners is currently somewhat limited. Despite current
limitations, some learners not yet supported natively in `sl3` can be used via
their corresponding wrappers in the `SuperLearner` package. `SuperLearner`
wrappers, screeners, and methods can all be used as `sl3` learners via
`Lrnr_pkg_SuperLearner`, `Lrnr_pkg_SuperLearner_screener`, and
`Lrnr_pkg_SuperLearner_method` respectively. To learn more about `SuperLearner`
wrappers, screeners, and methods, consult the documentation provided with that
R package. Here's an example of defining a `sl3` learner that uses the
`SL.glmnet` wrapper from `SuperLearner`.

```{r SuperLearner Wrapper}
lrnr_sl_glmnet <- make_learner(Lrnr_pkg_SuperLearner, "SL.glmnet")
```

In most cases, using these wrappers will not be as efficient as their native
`sl3` counterparts. If your favorite learner is missing from `sl3`, please
consider adding it by following the ["Defining New
Learners"](custom_lrnrs.html) vignette.

### Learner Parameters

In general, learners can be instantiated without providing any additional
parameters. We've tried to provide sensible defaults for each learner; however,
if you would like to modify the learners' behavior, you may do so by
instantiating learners with different parameters.

`sl3` Learners support some common parameters that work with all learners for
which they are applicable:

* `covariates`: subsets covariates before fitting. This allows different
  learners to be fit to the same task with different covariate subsets.

* `outcome_type`: overrides the `task$outcome_type`. This allows different
  learners to be fit to the same task with different outcome_types.

* `...`: abitrary parameters typically passed directly to the internal learner
  method. The documentation for each learner will direct to the appropriate
  function documentation for the learner method.

## Composing Learners

`sl3` defines two special learners, `Pipeline` and `Stack`, that allow learners
to be composed in a flexible manner.

### Pipelines

A pipeline is a set of learners to be fit _sequentially_, where the fit from one
learner is used to define the task for the next learner. There are many ways in
which a learner can define the task for the downstream learner. The `chain`
method defined by learners defines how this will work. Let's look at the example
of pre-screening variables. For now, we'll rely on a screener from the
`SuperLearner` package, although native `sl3` screening algorithms will be
implemented soon.

Below, we generate a screener object based on the `SuperLearner` function
`screen.corP` and fit it to our task. Inspecting the fit, we see that it
selected a subset of covariates:

```{r sl3-fit-screener, message=FALSE}
screen_cor <- Lrnr_pkg_SuperLearner_screener$new("screen.corP")
screen_fit <- screen_cor$train(task)
print(screen_fit)
```

Now, `chain` may be called on this learner fit to define a downstream task:

```{r sl3-chain-screener}
screened_task <- screen_fit$chain()
print(screened_task)
```

As with `predict`, we can omit a task from the call to `chain`, in which case
the call defaults to using the same task that was used for training. We can see
that the chained task reduces the covariates to the subset selected by the
screener. We can fit this new task using the `lrnr_glm` we defined above:

```{r sl3-glm-on-screened}
screened_glm_fit <- lrnr_glm$train(screened_task)
screened_preds <- screened_glm_fit$predict()
head(screened_preds)
```

The `Pipeline` class automates this process. It takes an arbitrary number of
learners and fits them sequentially, training and chaining each one in turn.
Since `Pipeline` is a learner like any other, it shares the same interface. We
can define a pipeline using `make_learner`, and use `train` and `predict` just
as we did before:

```{r sl3-define-pipeline}
sg_pipeline <- make_learner(Pipeline, screen_cor, lrnr_glm)
sg_pipeline_fit <- sg_pipeline$train(task)
sg_pipeline_preds <- sg_pipeline_fit$predict()
head(sg_pipeline_preds)
```

We see that the pipeline returns the same predictions as manually training `glm`
on the chained task from the screening learner.

### Stacks

Like `Pipeline`s, `Stack`s combine multiple learners. `Stack`s train learners
_simultaneously_, so that their predictions can be either combined or compared.
Again, `Stack` is just a special learner and so has the same interface as all
other learners:

```{r sl3-stack}
stack <- make_learner(Stack, lrnr_glm, sg_pipeline)
stack_fit <- stack$train(task)
stack_preds <- stack_fit$predict()
head(stack_preds)
```

Above, we've defined and fit a `stack` comprised of a simple `glm` learner as
well as a pipeline that combines a screening algorithm with that same learner.
We could have included any abitrary set of learners and pipelines, the latter of
which are themselves just learners. We can see that the `predict` method now
returns a matrix, with a column for each learner included in the stack.

### Cross-validation

Having defined a stack, we might want to compare the performance of learners in
the stack, which we may do using _cross-validation_. The `Lrnr_cv` learner wraps
another learner and performs training and prediction in a cross-validated
fashion, using separate training and validation splits as defined by
`task$folds`.

Below, we define a new `Lrnr_cv` object based on the previously defined `stack`
and train it and generate predictions on the validation set:

```{r sl3-cv-stack}
cv_stack <- Lrnr_cv$new(stack)
cv_fit <- cv_stack$train(task)
cv_preds <- cv_fit$predict()
```

We can also use the special `Lrnr_cv` function `cv_risk` to estimate
cross-validated risk values:

```{r sl3-cv-risk}
risks <- cv_fit$cv_risk(loss_squared_error)
print(risks)
```

In this example, we don't see much difference between the two learners,
suggesting the addition of the screening step in the pipeline learner didn't
improve performance much.

### The Super Learner Algorithm

We can combine all of the above elements, `Pipeline`s, `Stack`s, and
cross-validation using `Lrnr_cv`, to easily define a Super Learner. The Super
Learner algorithm works by fitting a "meta-learner", which combines predictions
from multiple stacked learners. It does this while avoiding overfitting by
training the meta-learner on validation-set predictions in a manner that is
cross-validated. Using some of the objects we defined in the above examples,
this becomes a very simple operation:

```{r sl3-metalearner-glm}
metalearner <- make_learner(Lrnr_nnls)
cv_task <- cv_fit$chain()
ml_fit <- metalearner$train(cv_task)
```

Here, we used a special learner, `Lrnr_nnls`, for the meta-learning step. This
fits a non-negative least squares meta-learner. It is important to note that any
learner can be used as a meta-learner.

The Super Learner finally produced is defined as a pipeline with the learner
stack trained on the full data and the meta-learner trained on the
validation-set predictions. Below, we use a special behavior of pipelines: if
all objects passed to a pipeline are learner fits (i.e., `learner$is_trained` is
`TRUE`), the result will also be a fit:

```{r sl3-define-SuperLearner}
sl_pipeline <- make_learner(Pipeline, stack_fit, ml_fit)
sl_preds <- sl_pipeline$predict()
head(sl_preds)
```

A Super Learner may be fit in a more streamlined manner using the `Lrnr_sl`
learner. For simplicity, we will use the same set of learners and meta-learning
algorithm as we did before:

```{r sl3-Lrnr_sl}
sl <- Lrnr_sl$new(learners = stack,
                  metalearner = metalearner)
sl_fit <- sl$train(task)
lrnr_sl_preds <- sl_fit$predict()
head(lrnr_sl_preds)
```

We can see that this generates the same predictions as the more hands-on
definition above.

## Computation with `delayed`

Fitting a Super Learner is composed of many different training and prediction
steps, as the procedure requires that the learners in the stack and the
meta-learner be fit on cross-validation folds and on the full data. For large
datasets, this can be extremely time-consuming. To alleviate this complication,
we've developed a specialized parallelization framework `delayed` that
parallelizes across these tasks in a way that takes into account their
inter-dependent nature. Consider a Super Learner with three learners:

```{r sl3-delayed-sl}
lrnr_rf <- make_learner(Lrnr_randomForest)
lrnr_glmnet <- make_learner(Lrnr_glmnet)
sl <- Lrnr_sl$new(learners = list(lrnr_glm, lrnr_rf, lrnr_glmnet),
                  metalearner = metalearner)
```

We can plot the network of tasks required to train this Super Learner:

```{r sl3-delayed-plot}
delayed_sl_fit <- delayed_learner_train(sl, task)
plot(delayed_sl_fit)
```

`delayed` then allows us to parallelize the procedure across these tasks using
the [`future`](https://github.com/HenrikBengtsson/future) package. For more
information on specifying `future` `plan`s for parallelization, see the
documentation of the [`future`](https://github.com/HenrikBengtsson/future)
package. Performance comparisons can be found in the ["SuperLearner
Benchmarks"](SuperLearner_benchmarks.html) vignette that accompanies this
package. This feature is currently experimental and hasn't yet been throughly
tested on a range of parallel backends.

---

## Session Information

```{r sessionInfo, echo=FALSE}
sessionInfo()
```

---

## References

