---
title: "SuperLearner Benchmarks"
author: "Jeremy Coyle"
date: "10/5/2017"
output: html_document
---

```{r setup, include=FALSE, results='hide'}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
library(sl3)
library(delayed)
library(SuperLearner)
library(future)
library(ggplot2)
library(data.table)
library(stringr)
library(scales)
```
## Test Setup

### Session Information

```{r sessionInfo, echo=FALSE, results="asis"}
sessionInfo()
```

### Test System

```{r systemInfo, echo=FALSE, results="asis"}
uname <- system("uname -a", intern = TRUE)
os <- sub(" .*", "", uname)
if(os=="Darwin"){
  cpu_model <- system("sysctl -n machdep.cpu.brand_string", intern = TRUE)
  cpus_physical <- as.numeric(system("sysctl -n hw.physicalcpu", intern = TRUE))
  cpus_logical <- as.numeric(system("sysctl -n hw.logicalcpu", intern = TRUE))
  cpu_clock <- system("sysctl -n hw.cpufrequency_max", intern = TRUE)
  memory <- system("sysctl -n hw.memsize", intern = TRUE)
} else if(os=="Linux"){
  cpu_model <- system("lscpu | grep 'Model name'", intern = TRUE)
  cpu_model <- gsub("Model name:[[:blank:]]*","", cpu_model)
  cpus_logical <- system("lscpu | grep '^CPU(s)'", intern = TRUE)
  cpus_logical <- as.numeric(gsub("^.*:[[:blank:]]*","", cpus_logical))
  tpc <- system("lscpu | grep '^Thread(s) per core'", intern = TRUE)
  tpc <- as.numeric(gsub("^.*:[[:blank:]]*","", tpc))
  cpus_physical <- cpus_logical/tpc
  cpu_clock <- as.numeric(gsub("GHz","",gsub("^.*@","",cpu_model)))*10^9
  memory <- system("cat /proc/meminfo | grep '^MemTotal'", intern = TRUE)
  memory <- as.numeric(gsub("kB","",gsub("^.*:","",memory)))*2^10
} else {
  stop("unsupported OS")
}
```

* CPU model: `r cpu_model`
* Physical cores: `r as.numeric(cpus_physical)`
* Logical cores: `r as.numeric(cpus_logical)`
* Clock speed: `r as.numeric(cpu_clock)/10^9`GHz
* Memory: `r round(as.numeric(memory)/2^30, 1)`GB

### Test Data

```{r data_setup, echo=TRUE, results="hide"}

data(cpp)
cpp <- cpp[!is.na(cpp[, "haz"]), ]
covars <- c("apgar1", "apgar5", "parity", "gagebrth", "mage", "meducyrs", "sexn")
cpp[is.na(cpp)] <- 0
cpp <- cpp[sample(nrow(cpp),10000,replace=T),]
# cpp <- cpp[1:150, ]
outcome <- "haz"


task <- sl3_Task$new(cpp, covariates = covars, outcome = outcome, outcome_type="continuous")

```

* Number of observations: `r nrow(task$X)`
* Number of covariates: `r ncol(task$X)`

### Test Descriptions

#### `sl3` with Legacy `SuperLearner` Wrappers
```{r sl3_legacy_setup, echo=TRUE}
sl_glmnet <- Lrnr_pkg_SuperLearner$new("SL.glmnet")
sl_random_forest <- Lrnr_pkg_SuperLearner$new("SL.randomForest")
sl_glm <- Lrnr_pkg_SuperLearner$new("SL.glm")
nnls_lrnr <- Lrnr_nnls$new()

sl3_legacy <- Lrnr_sl$new(list(sl_random_forest, sl_glmnet, sl_glm), nnls_lrnr)
```


#### `sl3` with Improved Wrappers
```{r sl3_improved_setup, echo=TRUE}
lrnr_glmnet <- Lrnr_glmnet$new()
random_forest <- Lrnr_randomForest$new()
glm_fast <- Lrnr_glm_fast$new()
nnls_lrnr <- Lrnr_nnls$new()

sl3_improved <- Lrnr_sl$new(list(random_forest, lrnr_glmnet, glm_fast), nnls_lrnr)
```

#### Legacy `SuperLearner`

```{r legacy_SuperLearner, echo=TRUE, message=FALSE}
time_SuperLearner_sequential <- system.time({
  SuperLearner(task$Y, as.data.frame(task$X), newX = NULL, family = gaussian(), 
               SL.library=c("SL.glmnet","SL.randomForest","SL.glm"),
               method = "method.NNLS", id = NULL, verbose = FALSE,
               control = list(), cvControl = list(), obsWeights = NULL, 
               env = parent.frame())
})

options(mc.cores=cpus_physical)
time_SuperLearner_multicore <- system.time({
  mcSuperLearner(task$Y, as.data.frame(task$X), newX = NULL, family = gaussian(), 
               SL.library=c("SL.glmnet","SL.randomForest","SL.glm"),
               method = "method.NNLS", id = NULL, verbose = FALSE,
               control = list(), cvControl = list(), obsWeights = NULL, 
               env = parent.frame())
})
```
## Results


```{r eval, echo=FALSE, results="hide", message=FALSE}
plan(sequential)
test <- delayed_learner_train(sl3_legacy, task)
time_sl3_legacy_sequential <- system.time({
  sched <- Scheduler$new(test, SequentialJob)
  cv_fit <- sched$compute()
})

test <- delayed_learner_train(sl3_improved, task)
time_sl3_improved_sequential <- system.time({
  sched <- Scheduler$new(test, SequentialJob)
  cv_fit <- sched$compute()
})

plan(multicore, workers=cpus_logical)
test <- delayed_learner_train(sl3_legacy, task)
time_sl3_legacy_multicore_ht <- system.time({
  sched <- Scheduler$new(test, FutureJob, nworkers=cpus_logical, verbose = FALSE)
  cv_fit <- sched$compute()
})

test <- delayed_learner_train(sl3_improved, task)
time_sl3_improved_multicore_ht <- system.time({
  sched <- Scheduler$new(test, FutureJob, nworkers=cpus_logical, verbose = FALSE)
  cv_fit <- sched$compute()
})

test <- delayed_learner_train(sl3_legacy, task)
time_sl3_legacy_multicore <- system.time({
  sched <- Scheduler$new(test, FutureJob, nworkers=cpus_physical, verbose = FALSE)
  cv_fit <- sched$compute()
})

test <- delayed_learner_train(sl3_improved, task)
time_sl3_improved_multicore <- system.time({
  sched <- Scheduler$new(test, FutureJob, nworkers=cpus_physical, verbose = FALSE)
  cv_fit <- sched$compute()
})

plan(multisession, workers=cpus_physical)
test <- delayed_learner_train(sl3_legacy, task)
time_sl3_legacy_multisession <- system.time({
  sched <- Scheduler$new(test, FutureJob, nworkers=cpus_physical, verbose = FALSE)
  cv_fit <- sched$compute()
})

test <- delayed_learner_train(sl3_improved, task)
time_sl3_improved_multisession <- system.time({
  sched <- Scheduler$new(test, FutureJob, nworkers=cpus_physical, verbose = FALSE)
  cv_fit <- sched$compute()
})


```

```{r results, echo=FALSE}

results <- rbind(time_sl3_legacy_sequential, time_sl3_legacy_multicore, 
                 time_sl3_legacy_multicore_ht, time_sl3_legacy_multisession,
                 time_sl3_improved_sequential, time_sl3_improved_multicore, 
                 time_sl3_improved_multicore_ht, time_sl3_improved_multisession,
                 time_SuperLearner_sequential, time_SuperLearner_multicore
                )
test <- rownames(results)

results <- as.data.table(results)

invisible(results[, test := gsub("time_", "", test)])
invisible(results[, improved:=str_detect(test, "improved")])
invisible(results[, parallel:=!str_detect(test, "sequential")])
results <- results[order(results$elapsed)]
invisible(results[, test := factor(test,levels=test)])
breaks=2^(-20:20)
ggplot(results, aes(y=test, x=elapsed, color=factor(improved), shape=factor(parallel)))+geom_point(size=3)+
  xlab("Time (seconds) -- log scale")+ylab("Test")+theme_bw()+
  scale_shape_discrete("Parallel Computation")+scale_color_discrete("Improved Learners")+
  scale_x_continuous(trans = log2_trans(), breaks=breaks)+ annotation_logticks(base=2, sides="b")  

```
